---
title: "Literature2"
author: "Marianna"
format: html
editor: visual
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(litsearchr)
library(dplyr)
library(ggplot2)
library(ggraph)
library(igraph)
library(readr)
library(bibliometrix)
library(scholar)
library(citationchaser)

```

Our topic lies in the intersection of policy diffusion, innovation and public policy. Hence, we draw from the policy diffusion theories from Political Science, the literature on the policy reforms - especially on public goods and services - from Economics. Last, insights on governance, coordination and costs will be also drawn from Public Administration. The combination of these fields allows as to explain this research from a multi-model point of view.

To position this research, we conduct first a bibliometric analysis. This way we can explore the research field. As in methodologies, such as meta-analysis or systematic review, the aim of this paper is to summarize the literature using large amounts of literature. As opposed to meta-analyses, bibliometric analysis looks at the structure and the components of a research area through performance analysis and science mapping.

```{r}
#get diffusion data from lens.org
M <- convert2df(file="diffusion.csv", dbsource="lens", format="csv")
results <- biblioAnalysis(M, sep = ";")


Packages <- c("dplyr", "httr", "jsonlite")
lapply(Packages, library, character.only = TRUE)

token<-"QSL9Q9f9FwAvGAh51XaO9vTx9dTTOfBjVKG08I5lWajj5e4N6mvE"
max_results <- 1000

getLensData<- function(token, query){
  url <- 'https://api.lens.org/scholarly/search'
  headers <- c('Authorization' = token, 'Content-Type' = 'application/json')
  httr::POST(url = url, add_headers(.headers=headers), body = query)
}


request <- paste0('{
	"query": "(abstract:(policy diffusion) AND field_of_study: (Economics OR Econometrics OR (Local government) OR (Political economy) OR (Policy analysis) OR(Political science) OR (Public administration)))",
	"size": "',max_results,'",
	"scroll": "2m"
}')


#"Econometrics", "Economic evaluation", "Economic geography", "Economics", "Economy", "Government", "Local government", "Political economy", "Policy analysis", "Political science", "Public administration", "Social network analysis", 
data <- getLensData(token, request)
record_json <- content(data, "text")
# convert json output from article search to list
record_list <- fromJSON(record_json) 
#convert it to a data frame
record_df <- data.frame(record_list) 
total<- record_list[["total"]]


# if a result contains more than the max number of records per request, use cursor based pagination
if(total > max_results) {
  
  #calculate the number of queries needed for those with more than the max number of results
  sets <- ceiling(record_list[["total"]] / max_results) 
  
  # extract the scroll id from the query to go back to the same search
  scroll_id <- record_list[["scroll_id"]] 
  
  # loop through the sets of results needed to bring back all records into a data frame
  for (i in 2:sets){ 
    #extract the latest scroll_id from the last query
    scroll_id <- record_list[["scroll_id"]] 
    
    # new query based on scroll_id and including 'include' for efficiency
    request <- paste0('{"scroll_id": "', 
                      scroll_id,
                      '"
                      }')
    
    # perform article search and extract text results
    data <- getLensData(token, request)
    record_json <- httr::content(data, "text")
    
    # convert json output from article search to list
    record_list <- jsonlite::fromJSON(record_json) 
    new_df <- data.frame(record_list)
    
    # bind the latest search data frame to the previous data frame
    record_df <- dplyr::bind_rows(record_df,new_df) 
  } 
}

clean_record<-record_df

clean_record<-clean_record %>% select (scroll_id:data.year_published,
                                       data.external_ids,
                                       data.authors:data.fields_of_study,
                                       data.references:data.scholarly_citations, data.keywords)


df_unlisted <- clean_record %>% 
unnest_wider(c(data.fields_of_study) , names_sep="_") 

df_unlisted<-df_unlisted %>% select(-data.fields_of_study_45, 
                                    -data.fields_of_study_44,
                                    -data.fields_of_study_43,
                                    -data.fields_of_study_42,
                                    -data.fields_of_study_41,
                                    -data.fields_of_study_40,
                                    -data.fields_of_study_39,
                                    -data.fields_of_study_38,
                                    -data.fields_of_study_37,
                                    -data.fields_of_study_36,
                                    -data.fields_of_study_35, 
                                    -data.fields_of_study_34,
                                    -data.fields_of_study_33,
                                    -data.fields_of_study_32,
                                    -data.fields_of_study_31,
                                    -data.fields_of_study_30,
                                    -data.fields_of_study_29,
                                    -data.fields_of_study_28,
                                    -data.fields_of_study_27,
                                    -data.fields_of_study_26,
                                    -data.fields_of_study_25, 
                                    -data.fields_of_study_24,
                                    -data.fields_of_study_23,
                                    -data.fields_of_study_22,
                                    -data.fields_of_study_21,
                                    -data.fields_of_study_20,
                                    -data.fields_of_study_19,
                                    -data.fields_of_study_18,
                                    -data.fields_of_study_17,
                                    -data.fields_of_study_16,
                                    -data.fields_of_study_15, 
                                    -data.fields_of_study_14,
                                    -data.fields_of_study_13,
                                    -data.fields_of_study_12,
                                    -data.fields_of_study_11)

df_unlisted<-df_unlisted %>% select(-data.source)
df_filtered<-df_unlisted %>% filter(data.fields_of_study_1=="Economics"|
                         data.fields_of_study_2=="Economics"|
                         data.fields_of_study_3=="Economics"|
                         data.fields_of_study_1=="Political science"|
                         data.fields_of_study_2=="Political science"|
                         data.fields_of_study_3=="Political science"|
                         data.fields_of_study_1=="Public administration"|
                         data.fields_of_study_2=="Public administration"|
                         data.fields_of_study_3=="Public administration"|
                         data.fields_of_study_1=="Local government"|
                         data.fields_of_study_2=="Local government"|
                         data.fields_of_study_3=="Local government")


doi<-df_filtered %>% unnest(data.external_ids, keep_empty = TRUE)
doi$value<-ifelse(doi$type=="coreid", 0, doi$value)
doi<-doi %>% unique()
doi$value<-ifelse(doi$type=="magid", 0, doi$value)
doi<-doi %>% unique()
doi<-spread(data=doi, key=type, value=value, fill=NA)
doi<-doi %>% select(-magid, -openalex, -pmcid, -pmid, -coreid, -data.keywords)
doi<-doi %>% unique()
doi$dup<-duplicated(doi$data.title)



```

```{r Descriptive Analysis, echo=TRUE, comment=NA}

options(width=100)
S <- summary(object = results, k = 10, pause = FALSE)

options(width=160)
M$TC<-M$Citing.Works.Count
M$TC<-as.numeric(M$TC)

results <- biblioAnalysis(M)
summary(results, k=10, pause=F, width=130)
plot(x=results, k=10, pause=F)


```

```{r Top-Authors’ Productivity over Time,  comment=NA}
authorProdOverTime(M, k = 10, graph = TRUE)


```

```{r biblionetwork}
#collaboration network
NetMatrix <- biblioNetwork(M, analysis = "collaboration",
network = "authors", sep = ";")
net <- networkPlot(NetMatrix, n = 30, type = "kamada", Title = "Collaboration",labelsize=0.5)

#co-citation network

NetMatrix <- biblioNetwork(M, analysis = "co-citation",
network = "references", sep = ";")
net <- networkPlot(NetMatrix, n = 30, type = "kamada", Title = "Co-Citation",labelsize=0.5)


#coupling network
#co-occurrenes netwrok

NetMatrix <- biblioNetwork(M, analysis = "co-occurrences",
network = "sources", sep = ";")
net <- networkPlot(NetMatrix, n = 30, type = "kamada", Title = "Co-Citation",labelsize=0.5)
```

```{r, comment=NA, fig.height=10, fig.width=10}
NetMatrix <- biblioNetwork(M, analysis = "co-citation", network = "references", sep = ";")
net=networkPlot(NetMatrix, n = 50, Title = "Co-Citation Network", type = "fruchterman", size.cex=TRUE, size=20, remove.multiple=FALSE, labelsize=1,edgesize = 10, edges.min=5)
netstat <- networkStat(NetMatrix)
summary(netstat,k=10)



```
