---
title: "Literature"
author: "Marianna Sebő"
format: html
editor: visual
bibliography: bibliography.bib
---

## Systematic Review

The aim of this article is to present the state of the art on Policy Diffusion and Innovation in Public Policy.

```{r}
#remotes::install_github("elizagrames/litsearchr", ref="main")
library(litsearchr)
library(dplyr)
library(ggplot2)
library(ggraph)
library(igraph)
library(readr)
```

Our topic lies in the intersection of policy diffusion, innovation and public policy. Hence, we draw from the policy diffusion theories from Political Science, the literature on the policy reforms - especially on public goods and services - from Economics. Last, insights on governance, coordination and costs will be also drawn from Public Administration. The combination of these fields allows as to explain this research from a multi-model point of view.

[@RN2587] In an overview on social networks and diffudion. Structures can influence economic behavior, diffusion of behavior and policies. Epidemiological models can be useful to model economic phenomena, as members interact. Relevant to our research, units or agent might be interested about the proportion of units adopting a given action. For their decision, when a given adoption threshold has been reached, their incentive might increase and they migh want to take an action  - same or different - from that of the neighbors. Agents that don't adopt early policies can free-ride on the information on the results of the actions of the neighbors. In empirical literature diffusion has been analyzed through the lenses of social networks on several fields. These include: marketing, labor economics, political economy, etc.

Glaeser, Sacerdote, and Scheinkman (1996) urban economics

Importance of social connections

"opinion leaders" in the study of voting

Whereas, as typically in economics, there is a growing literature with studies on correlations, casual inference might not be possible without a specific setting. Therefor several authors use experiments as in

Various field experiments, such as those by Duflo and Saez (2003), Karlan, Mobius, Rosenblat, and Szeidl (2009), Dupas (2010), Beaman and Magruder (2010), and Feigenberg, Field, and Pande (2010),

Another way to reach casual inference is using sctructural modeling. Banerjee, Chandrasekhar, Duflo, and Jackson (2010)

Newman, Barabasi & Watts
(2006),



The Handbook of Social Economics (forthcoming)



There are some popular
texts such as Watts (2003) and Barabasi (2004), as well as a history of thought of the sociology literature
by Freeman (2006) .

Goyal (2008)



Jackson (2008) synthesizes the analyses of networks from sociology, economics, statistical physics,
mathematics, and computer science.

Greenhouse gas emissions trading (ET) system has been an emerging policy to govern global issues. In this setting, multiple authorities are part of a governance system, whereas they scale and interconnectedness might differ, leading to a polycentric setting Ostrom 2010 a 2010b

Social network analysis arose in Sociology (e.g., Boissevain & Mitchell,
1973; Coleman, 1958; Scott, 1991; Wasserman & Faust, 1997; Wellman,
1983) but has recently emerged as a crucial methodology in political science as well (e.g., Bach & Newman, 2010; Cao, 2009, 2010; HafnerBurton, Kahler, & Montgomery, 2009; Hafner-Burton & Montgomery,
2006; Ward, Stovel, & Sacks, 2011).

The setting

The set $N = {1, ..., n}$ is the set of nodes that form part of the network. These nodes in our contexts are municipalities of Catalonia. Two nodes are either connected or not, - they cooperate or they don't. IMC is a reciprocal relationship, all the participants that form part of it have to agree to it. Such relationship can be modelled as un undirected network. Then, we have a graph $(N, g)$ that consists of a set of nodes $N = {1, ..., n}$ and a $ n x n$ matrix $g$ where $g_{ij}$ stands for the relationship between the nodes. Such relationship can be weighted or unweighted [@RN2590]. To represent the map of IMC in Catalonia as a network is appealing for several reasons. IMC is a relationship that migh be advantageous or disadvantageous. Such relationship can be quantified by common statistical parameter, e.g.: correlations, covariances, regression coefficients, partial correlations etc. 
Such connections can be seen as lin ks and modelled as paths through the network.

Partial correlation networks can provide valuable hypothesis generating structures, which may reflect potential causal effects to be further examined in terms of conditional independence (Pearl, 2000). When continuous data are multivariate normally distributed, analysing the partial correlations using the Gaussian graphical model (GGM; Costantini et al., 2015; Lauritzen, 1996) is appropriate. If the continuous data are not normally distributed then a transformation (e.g. nonparanormal transformation, Liu, Lafferty, & Wasserman, 2009) can be applied prior to applying the GGM. The GGM can also be used for ordinal data, wherein the network is based on the polychoric correlations instead of partial correlations (Epskamp, 2018). If all the research variables are binary, the Ising Model can be used (van Borkulo et al., 2014). When the data comprise a mixture of categorical and continuous variables, the Mixed Graphical Model can be used to estimate the PMRF (Haslbeck & Waldorp, 2016). Thus, networks can be estimated from various types of data in a flexible manner.


In order to conduct a bibliometric analysis on this topic first the Web of Science is used.

(AB=(policy diffusion)) OR TS=(policy diffusion) is put in the search field enabling the possibility of exact search. The 15,097 results are refined by choosing the research domain to be social sciences to 12,244. Web of Science Core collection 11,136 English 10,933. Major concepts were set to Government and Law, Population Studies, Economics, Public Health, Methods and Techniques, Sociology, Waste Management, Development, Transport and Circulation. Overall this lead to 553 results. The Mesh Qualifiers were set to Methods, Organization Administration, Economics, Statiscs Numerical Data, Trends, Legislations Jurisprudence, Standards, Analysis. 211 results were found this way. This has generated the file: wos.txt

In Scopus with policy diffusion 950 documentts. Limiting to Social Sciences, Business, Management and Accounting and Economics, Econometrics and finance 842. Limited to English papers 820

Scopus worked!

```{r}
S <- summary(object = results, k = 10, pause = FALSE)
plot(x = results, k = 10, pause = FALSE)


```

```{r}
topAU <- authorProdOverTime(M1, k = 10, graph = TRUE)

```

```{r}
naive_results <-import_results(file="scopus.bib")

keywords <- extract_terms(keywords=naive_results[, "keywords"], method="tagged", min_n=2, min_freq = 6)
title_terms<-extract_terms(text=naive_results[, "title"], method="fakerake", min_freq=4, min_n=2)
terms <- unique(c(keywords, title_terms))
docs <- paste(naive_results[, "title"], naive_results[, "abstract"])
dfm <- create_dfm(elements=docs, features=terms)
dfm[1:3, 1:4]
g <- create_network(dfm, min_studies=4)
ggraph(g, layout="stress") +
  coord_fixed() +
  expand_limits(x=c(-3, 3)) +
  geom_edge_link(aes(alpha=weight)) +
  geom_node_point(shape="circle filled", fill="white") +
  geom_node_text(aes(label=name), hjust="outward", check_overlap=TRUE) +
  guides(edge_alpha=FALSE)

strengths <- strength(g)

data.frame(term=names(strengths), strength=strengths, row.names=NULL) %>%
  mutate(rank=rank(strength, ties.method="min")) %>%
  arrange(strength) ->
  term_strengths

term_strengths

cutoff_fig <- ggplot(term_strengths, aes(x=rank, y=strength, label=term)) +
  geom_line() +
  geom_point() +
  geom_text(data=filter(term_strengths, rank>5), hjust="right", nudge_y=20, check_overlap=TRUE)

cutoff_fig
cutoff_cum <- find_cutoff(g, method="cumulative", percent=0.8)

cutoff_cum
cutoff_fig +
  geom_hline(yintercept=cutoff_cum, linetype="dashed")




```

```{r}
#remotes::install_github("massimoaria/bibliometrix")
library(bibliometrix)
biblioshiny()

```

```{r}
library(bibliometrix)
file<-"scopus.bib"
M<-convert2df(file = file, dbsource = "scopus", format= "bibtex")
results <- biblioAnalysis(M, sep = ";")
options(width=100)
S <- summary(object = results, k = 10, pause = FALSE)
plot(x = results, k = 10, pause = FALSE)
CR <- citations(M, field = "article", sep = ";")
cbind(CR$Cited[1:10])
CR <- citations(M, field = "author", sep = ";")
cbind(CR$Cited[1:10])
topAU <- authorProdOverTime(M, k = 10, graph = TRUE)

NetMatrix <- biblioNetwork(M, analysis = "co-occurrences", network = "keywords", sep = ";")

# Plot the network
net=networkPlot(NetMatrix, normalize="association", weighted=T, n = 30, Title ="Keyword Co-occurrences", type = "fruchterman", size=T,edgesize = 5,labelsize=0.7)

CS <- conceptualStructure(M,field="ID", method="CA", minDegree=4, clust=5, stemming=FALSE, labelsize=10, documents=10)



```

```{r}
# Create keyword co-occurrences network

NetMatrix <- biblioNetwork(M, analysis = "co-occurrences", network = "keywords", sep = ";")

# Plot the network
net=networkPlot(NetMatrix, normalize="association", weighted=T, n = 30, Title = "Keyword Co-occurrences", type = "fruchterman", size=T,edgesize = 5,labelsize=0.7)
```

```{r}
CS <- conceptualStructure(M,field="ID", method="CA", minDegree=4, clust=5, stemming=FALSE, labelsize=10, documents=10)

```

```{r}
# Create a historical citation network
options(width=130)
histResults<-histNetwork(M, min.citations =1, sep = ";")

```

```{r}
#Plot a historial co-citation network
net<-histPlot(histResults, n=15, size=10, labelsize=5)
```

Link: https://github.com/singh1985/bibliometix_june22/blob/main/bibliometrix_slides_ECU_15june.Rmd

```{r}
devtools::install_github("muschellij2/rscopus")


```

```{r}

```

```{r}
#using dimension
#search "public policy" AND "diffusion" AND "innovation"
#using second option to export
#now following "public policy" AND "diffusion" AND "innovation"

github_list <- c(
  "agoutsmedt/networkflow", # manipulating network
  "ParkerICI/vite" # needed for the spatialisation of the network
)
for (p in github_list) {
  if (gsub(".*/", "", p) %in% installed.packages() == FALSE) {
    devtools::install_github(p)
  }
  library(gsub(".*/", "", p), character.only = TRUE)
}

```

```{r}

devtools::install_github("ParkerICI/vite")



```

```{r}
#if severAL DOWNLOADS
#dimensions_data_1 <- read_csv(here(dimensions_path,
#                                "dimensions_dsge_data_2015-2022.csv"),
#                           skip = 1)
#dimensions_data_2 <- read_csv(here(dimensions_path,
#                                            "dimensions_dsge_data_1996-2014.csv"),
#                                       skip = 1)

#dimensions_data <- rbind(dimensions_data_1,
#                                  dimensions_data_2) %>% 
#  clean_names() # cleaning column names with janitor to transform them

dimensions_data<- read_csv(("Dimensions-Publication-2023-02-20_11-25-47.csv"), skip=1) %>% clean_names()

dimensions_data
```

```{r}
duplicated_articles <- dimensions_data %>%
  add_count(title) %>% 
  filter(n > 1) %>% 
  arrange(title, cited_references)

to_keep <- duplicated_articles %>% 
  group_by(title) %>% 
  slice_head(n = 1)

to_remove <- duplicated_articles %>% 
  filter(! publication_id %in% to_keep$publication_id)

dimensions_data <- dimensions_data %>% 
  filter(! publication_id %in% to_remove$publication_id)
```

```{r}
references_extract <- dimensions_data %>% 
  filter(! is.na(cited_references)) %>% 
  rename("citing_id" = publication_id) %>% # because the "publication_id" column is also the identifier of the reference
  select(citing_id, cited_references) %>% 
  separate_rows(cited_references, sep = ";(?=\\[)") %>%
  as_tibble

column_names <- c("authors",
                  "author_id",
                  "source",
                  "year",
                  "volume",
                  "issue",
                  "pagination",
                  "doi",
                  "publication_id",
                  "times_cited")

dimensions_direct_citation <- references_extract %>% 
  separate(col = cited_references, into = column_names, sep = "\\|")

head(dimensions_direct_citation, n = 5)

dimensions_references <- dimensions_direct_citation %>% 
  distinct(publication_id, .keep_all = TRUE) %>% 
  select(-citing_id)
```
